---
title: "First Assignment"
author: "Parsa Fouladi"
date: "2023-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence Intervals

### 1.1 In this assignment, our plan is to first explore the data and see which columns from the continuous variables look normally distributed.

```{r}
auto_df=read.csv('auto-mpg.csv')
```

```{r}
head(auto_df)
```

```{r}
summary(auto_df)
```

As you can see, the type of horsepower is written as 'character' which is quite odd. There should be a problematic value in the column that's causing this problem.

When we look at the data, we can see some of the rows has '?' as horsepower value.

```{r}
auto_df$horsepower.numerical=ifelse(auto_df$horsepower=="?",NA,auto_df$horsepower)
auto_df$horsepower.numerical<-as.numeric(auto_df$horsepower.numerical)
```

Now can plot the horsepower too.

```{r}
hist(auto_df$cylinders)
hist(auto_df$displacement)
hist(auto_df$weight)
hist(auto_df$acceleration)
hist(auto_df$model.year)
hist(auto_df$horsepower.numerical)
```

As you can see, among all the existing columns, the acceleration looks more normally distributed.

### 1.2 Now we will try to find the confidence interval (95%) for the mean of the acceleration column

```{r}
t.test(auto_df$acceleration)
```

As you can see, the confidence interval (95%) for the mean of the acceleration is between 15.3 and 15.84.

## Including Plotsacceleration
