---
title: "First Assignment"
author: "Parsa Fouladi"
date: "2023-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence Intervals

### 1.1 In this assignment, our plan is to first explore the data and see which columns from the continuous variables look normally distributed.

```{r}
auto_df=read.csv('auto-mpg.csv')
```

```{r}
head(auto_df)
```

```{r}
summary(auto_df)
```

As you can see, the type of horsepower is written as 'character' which is quite odd. There should be a problematic value in the column that's causing this problem.

When we look at the data, we can see some of the rows has '?' as horsepower value.

```{r}
auto_df$horsepower.numerical=ifelse(auto_df$horsepower=="?",NA,auto_df$horsepower)
auto_df$horsepower.numerical<-as.numeric(auto_df$horsepower.numerical)
```

Now can plot the horsepower too.

```{r}
hist(auto_df$cylinders)
hist(auto_df$displacement)
hist(auto_df$weight)
hist(auto_df$acceleration)
hist(auto_df$model.year)
hist(auto_df$horsepower.numerical)
```

As you can see, among all the existing columns, the acceleration looks more normally distributed.

### 1.2 Now we will try to find the confidence interval (95%) for the mean of the acceleration column

```{r}
t.test(auto_df$acceleration)
```

As you can see, the confidence interval (95%) for the mean of the acceleration is between 15.3 and 15.84.

## 2. CI for proportion of the cars

In this section, we are supposed to calculate the proportion of cars that are from the 80s in a subset that includes the model years range from the 70s and the 80s. Then we will try to find a 90 % condence interval for the proportion of cars from the 80s.

### 2.1 Proportion of the cars from 80s

```{r}
proportion=nrow(subset(auto_df,auto_df$model.year>=80))/nrow(auto_df)
proportion
```

### 2.2 Compute a 90 % confidence interval for the proportion of cars from the 80s

```{r}
prop.test(nrow(subset(auto_df,auto_df$model.year>=80)),nrow(auto_df),conf.level = 0.9)
```

As you can see the confidence interval is between 0.19 and 0.261. So this means that, we can say that we are 90% sure that the true proportion value is between 0..19 and 0.261.
